---
title: "One-Year-Ahead Predictions"
author: "Markus Min"
date: "`r Sys.Date()`"
output:
  html_document
---

Coming soon - one-year-ahead predictive performance compared across all stocks using four models:

1. Linear regression
2. GAM
3. Random forest
4. Neural networks

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE)
```

```{r load_data_functions}
library(here)
library(kableExtra)
source(here::here("R", "functions", "load_reformat_data.R"))

# get number of cores for parallelization
cores <- parallel::detectCores()
```

```{r functions_block}
# establish training/validation/testing splits
split_training_testing_one_yr_ahead <- function(data) {
  # drop all columns that aren't ID, features, or outcome
  data %>%
    dplyr::select(-c("one_sd_boom_bust", "Parm_StDev", "recr_scaled")) -> data
  
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # First, we will split our data into training and testing data. The testing
  # data is the last ten years of our dataset; the training data is the rest
  
  # Second, we will take our training data and use rolling_origin() to create folds
  # within it; following the workflow of Allen Akselrud 2024, we will start with
  # the first ten years as our first set of analysis data, and continue to predict
  # one year ahead
  
  # Here, we are going to use essentially rolling LFO-CV twice: once for
  
  # create the resamples for ASSESSMENT from the TRAINING data
  assessment_resamples <- rolling_origin(
    subset(data, !(Yr %in% last_10_yrs)),
    # don't include the testing data!
    initial = 10,
    # number of initial years
    assess  = 1,
    # predict 1 future year
    cumulative = TRUE,
    skip = 0
  )
  
  # create the resamples for TESTING
  testing_resamples <- rolling_origin(
    data,
    initial = nrow(subset(data, !(
      Yr %in% last_10_yrs
    ))),
    # number of initial years
    assess  = 1,
    # predict 1 future year
    cumulative = TRUE,
    skip = 0
  )
  
  # create a table that has the truth (Value) for the left out years
  testing_resamples_df <- testing_resamples %>%
    mutate(
      assessment_data = map(splits, assessment),
      .row = map_int(splits, ~ as.integer(assessment(.x)$Yr - min(data$Yr) + 1))
    ) %>%
    dplyr::select(id, assessment_data, .row) %>%
    unnest(assessment_data) %>%
    dplyr::select(id, Value, .row)
  
  return(
    list(
      assessment_resamples = assessment_resamples,
      testing_resamples = testing_resamples,
      testing_resamples_df = testing_resamples_df
    )
  )
  
}

# fit a null model
fit_null_model <- function(data, testing_resamples_df){
  
    # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # Use same null model as Ward et al. 2024:
  # The null model consisted of using the  historical mean preceding each holdout 
  # point (equivalent to fitting  an intercept only model).
  # this will be very close to assuming a recDev of zero, but not exactly
  
  # Calculate class proportions from training data
  null_model_pred <- data.frame(Yr = last_10_yrs, .pred_Value = rep(NA, 10))
  for (i in last_10_yrs){
    pred_val <- mean(subset(data, !(Yr %in% i:max(data$Yr)))$Value)
    null_model_pred[null_model_pred$Yr == i,]$.pred_Value <- pred_val
  }
  
  # Construct a null prediction tibble using training proportions
  null_model_pred <- cbind(testing_resamples_df, null_model_pred)
  
  # Calculate null RMSE + rsq
  null_model_pred %>%
    rmse(truth = Value,
                .pred_Value) %>% 
    mutate(model = "null") -> null_rmse
  
  null_model_pred %>%
    rsq(truth = Value,
        .pred_Value) %>% 
    mutate(model = "null") -> null_rsq
  
  # start a table to compare models with the null metrics table
  null_metrics <- bind_rows(null_rmse, null_rsq)
  
  return(null_metrics)
}

## Function to fit a lm model for a given set of predictors
fit_one_lm_lfo <- function(data, pred_set, resamples){
  
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # Build the formula
  lm_f <- as.formula(paste0("Value ~ ", paste(pred_set[[1]], collapse = " + ")))
  
  # Set up the model
  lm_mod <- linear_reg() %>% 
    set_engine("lm")
  
  # Set up the recipe
  lm_recipe <- recipe(lm_f, data = subset(data, !(Yr %in% last_10_yrs)))

  # package these together into a workflow for the model
  workflow() %>%
    add_model(lm_mod) %>% 
    add_recipe(lm_recipe)  -> lm_workflow
  
  # Fit and evaluate using LFO-CV
  # note that this is unable to compute rsq on a single left-out value,
  # so we will calculate our metrics after the function is run
  fit_resamples(
    lm_workflow,
    resamples = resamples,
    metrics = metric_set(rmse),
    control = control_resamples(save_pred = TRUE)
  ) -> lm_res
  
  return(lm_res)
}

# fit a multiple linear regression
fit_lm <- function(data, assessment_resamples){
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  #### Fit multiple linear regression ####
  # drop all columns that aren't ID, features, or outcome
  data %>%
    dplyr::select(-c("one_sd_boom_bust", "Parm_StDev", "recr_scaled")) -> data
  
  ### Generate all possible combinations of 1, 2, and 3 predictors
  
  predictors <- colnames(dplyr::select(data, -c("Yr", "Value")))
  
  # use the map function
  predictor_combos <- bind_rows(map(1:3, ~ combn(predictors, .x, simplify = FALSE) %>% 
    map(~ tibble(predictors = list(.x))))
  ) %>% 
    mutate(model_id = row_number())

  # Fit all models
  predictor_combos %>%
    mutate(lfo_cv_fit = map(predictors, \(x) fit_one_lm_lfo(data, x, assessment_resamples))) -> lm_results
    # mutate(lfo_cv_fit = map(predictor_combos$predictors, ~fit_one_lm_lfo(.x, assessment_resamples))) -> lm_results
  
  lm_results %>% 
    mutate(
      # RMSE from fold-level evaluation (already computed per fold)
      # this is calculated as an average for each held out year
      rmse = map_dbl(lfo_cv_fit, ~ collect_metrics(.x) %>% 
                       filter(.metric == "rmse") %>% 
                       pull(mean)),
      # rsq computed across all pooled held-out predictions
      # this is calculated
      rsq = map_dbl(lfo_cv_fit, ~ collect_predictions(.x) %>% 
                      rsq(truth = Value, estimate = .pred) %>% 
                      pull(.estimate)),
      n_predictors = map_int(predictors, length),
      predictor_names = map_chr(predictors, ~ paste(.x, collapse = " + "))
    ) %>% 
    dplyr::select(model_id, n_predictors, predictor_names, rmse, rsq) -> lm_metrics
  
  # extract the best model based on RMSE
  lm_metrics %>% 
    arrange(rmse) %>% 
    head(1) -> best_fit_lm
  
  ### The last fit - fit the best model to combined training + validation data, evaluate on testing
  
  # Build the last
  lm_last_f <- as.formula(paste0("Value ~ ", paste(best_fit_lm$predictor_names, collapse = " + ")))
  
  # the last recipe
  lm_last_recipe <- recipe(lm_last_f, data = data)
  
  # the last workflow
  # update the recipe with the new formula
  lm_mod <- linear_reg() %>% 
    set_engine("lm")
    
  workflow() %>%
    add_model(lm_mod) %>% 
    add_recipe(lm_last_recipe)  -> last_lm_workflow
  
  # the last fit
  # first, we need to make a split that has all training data and all testing data separated
  data_split <- make_splits(x = list(analysis = 1:(nrow(data)-10),
                                          assessment = (nrow(data)-9):nrow(data)),
                                 data = data)
  last_lm_fit <- last_lm_workflow %>% 
    last_fit(data_split)
  
  # evaluate performance
  last_lm_fit %>% 
    collect_metrics() %>% 
    mutate(model = paste0("lm(", deparse(lm_last_f), ")")) %>%
    dplyr::select(-.config) -> last_lm_fit_metrics
  
  return(last_lm_fit_metrics)

}

## Function to fit a gam model for a given set of predictors
fit_one_gam_lfo <- function(data, pred_set, resamples){
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # Build the formulas - two in this case for GAMs
  gam_f_splines <- as.formula(paste0("Value ~ ", paste("s(", pred_set[[1]], ", k = 3)", collapse = " + ")))
  
  gam_f <- as.formula(paste0("Value ~ ", paste(pred_set[[1]], collapse = " + ")))

  # Set up the model
  gam_mod <- gen_additive_mod() %>% 
    set_engine("mgcv", num.threads = cores) %>% 
    set_mode("regression")
  
  # package these together into a workflow for the model
  workflow() %>%
    add_model(gam_mod, formula = gam_f_splines) %>% 
    add_formula(gam_f) %>% 
    fit(data = subset(data, !(Yr %in% last_10_yrs)))  -> gam_workflow
  
  # Fit and evaluate using LFO-CV
  # note that this is unable to compute rsq on a single left-out value,
  # so we will calculate our metrics after the function is run
  fit_resamples(
    gam_workflow,
    resamples = resamples,
    metrics = metric_set(rmse),
    control = control_resamples(save_pred = TRUE)
  ) -> gam_res
  
  return(gam_res)
}

# fit a GAM
fit_gam <- function(data, assessment_resamples){
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # drop all columns that aren't ID, features, or outcome
  data %>%
    dplyr::select(-c("one_sd_boom_bust", "Parm_StDev", "recr_scaled")) -> data
  
  ### Generate all possible combinations of 1, 2, and 3 predictors
  
  predictors <- colnames(dplyr::select(data, -c("Yr", "Value")))
  
  # use the map function
  predictor_combos <- bind_rows(map(1:3, ~ combn(predictors, .x, simplify = FALSE) %>%
    map(~ tibble(predictors = list(.x))))
  ) %>%
    mutate(model_id = row_number())

  # Fit all models
  predictor_combos %>%
  mutate(lfo_cv_fit = map(predictors, \(x) fit_one_gam_lfo(data, x, assessment_resamples))) -> gam_results
  
  gam_results %>% 
  mutate(
    # RMSE from fold-level evaluation (already computed per fold)
    # this is calculated as an average for each held out year
    rmse = map_dbl(lfo_cv_fit, ~ collect_metrics(.x) %>% 
                     filter(.metric == "rmse") %>% 
                     pull(mean)),
    # rsq computed across all pooled held-out predictions
    # this is calculated
    rsq = map_dbl(lfo_cv_fit, ~ collect_predictions(.x) %>% 
                    rsq(truth = Value, estimate = .pred) %>% 
                    pull(.estimate)),
    n_predictors = map_int(predictors, length),
    predictor_names = map_chr(predictors, ~ paste(.x, collapse = " + "))
  ) %>% 
  dplyr::select(model_id, n_predictors, predictor_names, rmse, rsq) -> gam_metrics
  
  # extract the best model based on RMSE
  gam_metrics %>% 
  arrange(rmse) %>% 
  head(1) -> best_fit_gam
  
  ### The last fit - fit the best model to combined training + validation data, evaluate on testing
  
  # Build the last model
  gam_last_f_splines <- as.formula(paste0("Value ~ ", paste("s(", best_fit_gam$predictor_names, ", k = 3)", collapse = " + ")))
  gam_last_f <- as.formula(paste0("Value ~ ", paste(best_fit_gam$predictor_names, collapse = " + ")))
  
  
  # the last workflow
  # update the workflow with the new formula
  # Set up the model
  gam_mod <- gen_additive_mod() %>% 
    set_engine("mgcv", num.threads = cores) %>% 
    set_mode("regression")
  
  workflow() %>%
    add_model(gam_mod, formula = gam_last_f_splines) %>% 
    add_formula(gam_last_f) -> last_gam_workflow
  
  
  # the last fit
  # first, we need to make a split that has all training data and all testing data separated
  data_split <- make_splits(x = list(analysis = 1:(nrow(data)-10),
                                        assessment = (nrow(data)-9):nrow(data)),
                               data = data)
  last_gam_fit <- last_gam_workflow %>% 
  last_fit(data_split)
  
  # evaluate performance
  last_gam_fit %>% 
  collect_metrics() %>% 
  mutate(model = paste0("gam(", deparse(gam_last_f), ")")) %>%
  dplyr::select(-.config) -> last_gam_fit_metrics
  
  return(last_gam_fit_metrics)
  
}

# tune + fit a rf
fit_rf <- function(data, assessment_resamples){
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
    # drop all columns that aren't ID, features, or outcome
  data %>%
    dplyr::select(-c("one_sd_boom_bust", "Parm_StDev", "recr_scaled")) -> data
  
  # set up the model
  rf_mod <- 
    rand_forest(mtry = tune(), min_n = tune(), trees = tune()) %>% 
    set_engine("ranger", num.threads = cores) %>% 
    set_mode("regression")
  
  # set up the recipe - formula + code columns
  rf_recipe <- recipe(Value ~., data = subset(data, !(Yr %in% last_10_yrs))) %>% 
    update_role(Yr, new_role = "ID")
  
  # package these together into a workflow for the model,
  workflow() %>%
    add_model(rf_mod) %>% 
    add_recipe(rf_recipe)  -> rf_workflow
  
  rf_grid <- grid_regular(
    mtry(range = c(2, 10)),        # can't exceed number of predictors
    min_n(range = c(2, 10)), # keep well below number of training rows
    trees(range = c(500, 2500)),
    # levels = c(5, 5, 25) # try more trees than mtry or min_n - takes forever
    levels = c(5, 5, 5)
  )
  
  # tune the hyperparameters on the assessment resamples
  rf_res <- 
    rf_workflow %>% 
    tune_grid(assessment_resamples,
              grid = rf_grid,
              control = control_grid(save_pred = TRUE),
              metrics = metric_set(rmse))
  
  # select the best model according to RMSE
  rf_best <- rf_res %>% 
    select_best(metric = "rmse")
  
  autoplot(rf_res)
  
  # evaluate model on the held-out testing data and store rmse
  ### The last fit - fit the best model to combined training + validation data, evaluate on testing
  
  # the last model
  last_rf_mod <- rand_forest(mtry = rf_best$mtry, min_n = rf_best$min_n, trees = rf_best$trees) %>% 
    set_engine("ranger", num.threads = cores, importance = "impurity") %>% 
    set_mode("regression")
  
  # the last workflow
  last_rf_workflow <- 
    rf_workflow %>% 
    update_model(last_rf_mod)
  
  # the last fit
  # first, we need to make a split that has all training data and all testing data separated
  data_split <- make_splits(x = list(analysis = 1:(nrow(data)-10),
                                          assessment = (nrow(data)-9):nrow(data)),
                                 data = data)
  last_rf_fit <- last_rf_workflow %>% 
    last_fit(data_split)
  
  # evaluate performance
  last_rf_fit %>% 
    collect_metrics() %>% 
    mutate(model = "random forest") %>% 
    dplyr::select(-.config) -> last_rf_fit_metrics
  
  return(last_rf_fit_metrics)
}


## Function to fit a nn model for a given set of predictors
fit_one_nn_lfo <- function(data, pred_set, resamples){
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # Build the formula
  nn_f <- as.formula(paste0("Value ~ ", paste(pred_set[[1]], collapse = " + ")))
  
  # Set up the recipe
  nn_recipe <- recipe(nn_f, data = subset(data, !(Yr %in% last_10_yrs)))
  
  # set model specifications
  nn_spec <- # mlp(epochs = 100, hidden_units = 2, penalty = 0.01, learn_rate = 0.1) %>% 
    mlp(epochs = 50, penalty = 0, hidden_units = 3) %>% 
    # set_engine("brulee", validation = 0) %>% 
    set_engine("nnet") %>% 
    set_mode("regression")
  
  # set up the workflow
  nn_workflow <- nn_recipe %>% 
    workflow(nn_spec)
  
  # Fit and evaluate using LFO-CV
  # note that this is unable to compute rsq on a single left-out value,
  # so we will calculate our metrics after the function is run
  # mlp_reg_fit <- nn_spec |> fit(nn_f, data = subset(data, !(Yr %in% last_10_yrs)))
  # 3-3-1 network with 26 weights
  
  fit_resamples(
    nn_workflow,
    resamples = resamples,
    metrics = metric_set(rmse),
    control = control_resamples(save_pred = TRUE)
  ) -> nn_res
  
  return(nn_res)
}

# tune + fit a neural network
fit_nn <- function(data, assessment_resamples){
  # get first ten years
  first_10_yrs <- (min(data$Yr):(min(data$Yr) + 9))
  
  # get last ten years
  last_10_yrs <- (max(data$Yr) - 9):max(data$Yr)
  
  # drop all columns that aren't ID, features, or outcome
  data %>%
    dplyr::select(-c("one_sd_boom_bust", "Parm_StDev", "recr_scaled")) -> data
  
    ### Generate all possible combinations of 1, 2, and 3 predictors
  
  predictors <- colnames(dplyr::select(data, -c("Yr", "Value")))
  
  # create combinations of 3 for initial testing
  NN_predictor_combos <- bind_rows(map(3, ~ combn(predictors, .x, simplify = FALSE) %>% 
                                         map(~ tibble(predictors = list(.x))))
  ) %>% 
    mutate(model_id = row_number())
  
  
  # Fit all models
  NN_predictor_combos %>%
    mutate(lfo_cv_fit = map(predictors, \(x) fit_one_nn_lfo(data, x, assessment_resamples))) -> nn_results

  
  nn_results %>% 
    mutate(
      # RMSE from fold-level evaluation (already computed per fold)
      # this is calculated as an average for each held out year
      rmse = map_dbl(lfo_cv_fit, ~ collect_metrics(.x) %>% 
                       filter(.metric == "rmse") %>% 
                       pull(mean)),
      # rsq computed across all pooled held-out predictions
      # this is calculated
      rsq = map_dbl(lfo_cv_fit, ~ collect_predictions(.x) %>% 
                      rsq(truth = Value, estimate = .pred) %>% 
                      pull(.estimate)),
      n_predictors = map_int(predictors, length),
      predictor_names = map_chr(predictors, ~ paste(.x, collapse = " + "))
    ) %>% 
    dplyr::select(model_id, n_predictors, predictor_names, rmse, rsq) -> nn_metrics
  
  # extract the best model based on RMSE
  nn_metrics %>% 
    arrange(rmse) %>% 
    head(1) -> best_fit_nn
  
  ### The last fit - fit the best model to combined training + validation data, evaluate on testing
  
  # Build the last
  nn_last_f <- as.formula(paste0("Value ~ ", paste(best_fit_nn$predictor_names, collapse = " + ")))
  
  # the last recipe
  nn_last_recipe <- recipe(nn_last_f, data = data)
  
  # the last workflow
  nn_spec <- # mlp(epochs = 100, hidden_units = 2, penalty = 0.01, learn_rate = 0.1) %>% 
    mlp(epochs = 50, penalty = 0, hidden_units = 3) %>% 
    # set_engine("brulee", validation = 0) %>% 
    set_engine("nnet") %>% 
    set_mode("regression")
  
  nn_workflow <- nn_recipe %>% 
    workflow(nn_spec)
  
  last_nn_workflow <- 
    nn_workflow %>% 
    update_recipe(nn_last_recipe)
  
  # the last fit
  # first, we need to make a split that has all training data and all testing data separated
  data_split <- make_splits(x = list(analysis = 1:(nrow(data)-10),
                                          assessment = (nrow(data)-9):nrow(data)),
                                 data = data)
  last_nn_fit <- last_nn_workflow %>% 
    last_fit(data_split)
  
  # evaluate performance
  last_nn_fit %>% 
    collect_metrics() %>% 
    mutate(model = paste0("nn(", deparse(nn_last_f), ")")) %>%
    dplyr::select(-.config) -> last_nn_fit_metrics
  
  return(last_nn_fit_metrics)
  
}

```


## One-Year-Ahead Predictive Performance {.tabset .tabset-pills}

### Black Rockfish - Northern CA (2023 assessment)

```{r black_rf_nca_ml, cache = TRUE}
black_rf_nca_splits <- split_training_testing_one_yr_ahead(data = black_rf_nca)

black_rf_nca_null_metrics <- fit_null_model(data = black_rf_nca, testing_resamples_df = black_rf_nca_splits$testing_resamples_df)

black_rf_nca_lm_metrics <- fit_lm(data = black_rf_nca, assessment_resamples = black_rf_nca_splits$assessment_resamples)

black_rf_nca_gam_metrics <- fit_gam(data = black_rf_nca, assessment_resamples = black_rf_nca_splits$assessment_resamples)

black_rf_nca_rf_metrics <- fit_rf(data = black_rf_nca, assessment_resamples = black_rf_nca_splits$assessment_resamples)

black_rf_nca_nn_metrics <- fit_nn(data = black_rf_nca, assessment_resamples = black_rf_nca_splits$assessment_resamples)

black_rf_nca_model_comparison_table <- bind_rows(black_rf_nca_null_metrics,
                                              black_rf_nca_lm_metrics,
                                              black_rf_nca_gam_metrics,
                                              black_rf_nca_rf_metrics,
                                              black_rf_nca_nn_metrics)

black_rf_nca_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Black Rockfish (Northern CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Black Rockfish - Central CA (2023 assessment)

```{r black_rf_cca_ml, cache = TRUE}
black_rf_cca_splits <- split_training_testing_one_yr_ahead(data = black_rf_cca)

black_rf_cca_null_metrics <- fit_null_model(data = black_rf_cca, testing_resamples_df = black_rf_cca_splits$testing_resamples_df)

black_rf_cca_lm_metrics <- fit_lm(data = black_rf_cca, assessment_resamples = black_rf_cca_splits$assessment_resamples)

black_rf_cca_gam_metrics <- fit_gam(data = black_rf_cca, assessment_resamples = black_rf_cca_splits$assessment_resamples)

black_rf_cca_rf_metrics <- fit_rf(data = black_rf_cca, assessment_resamples = black_rf_cca_splits$assessment_resamples)

black_rf_cca_nn_metrics <- fit_nn(data = black_rf_cca, assessment_resamples = black_rf_cca_splits$assessment_resamples)

black_rf_cca_model_comparison_table <- bind_rows(black_rf_cca_null_metrics,
                                              black_rf_cca_lm_metrics,
                                              black_rf_cca_gam_metrics,
                                              black_rf_cca_rf_metrics,
                                              black_rf_cca_nn_metrics)

black_rf_cca_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Black Rockfish (Central CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Black Rockfish - Oregon (2023 assessment)

```{r black_rf_or_ml, cache = TRUE}
black_rf_or_splits <- split_training_testing_one_yr_ahead(data = black_rf_or)

black_rf_or_null_metrics <- fit_null_model(data = black_rf_or, testing_resamples_df = black_rf_or_splits$testing_resamples_df)

black_rf_or_lm_metrics <- fit_lm(data = black_rf_or, assessment_resamples = black_rf_or_splits$assessment_resamples)

black_rf_or_gam_metrics <- fit_gam(data = black_rf_or, assessment_resamples = black_rf_or_splits$assessment_resamples)

black_rf_or_rf_metrics <- fit_rf(data = black_rf_or, assessment_resamples = black_rf_or_splits$assessment_resamples)

black_rf_or_nn_metrics <- fit_nn(data = black_rf_or, assessment_resamples = black_rf_or_splits$assessment_resamples)

black_rf_or_model_comparison_table <- bind_rows(black_rf_or_null_metrics,
                                              black_rf_or_lm_metrics,
                                              black_rf_or_gam_metrics,
                                              black_rf_or_rf_metrics,
                                              black_rf_or_nn_metrics)

black_rf_or_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Black Rockfish (OR).") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Black Rockfish - Washington (2023 assessment)

```{r black_rf_wa, cache = TRUE}
black_rf_wa_splits <- split_training_testing_one_yr_ahead(data = black_rf_wa)

black_rf_wa_null_metrics <- fit_null_model(data = black_rf_wa, testing_resamples_df = black_rf_wa_splits$testing_resamples_df)

black_rf_wa_lm_metrics <- fit_lm(data = black_rf_wa, assessment_resamples = black_rf_wa_splits$assessment_resamples)

black_rf_wa_gam_metrics <- fit_gam(data = black_rf_wa, assessment_resamples = black_rf_wa_splits$assessment_resamples)

black_rf_wa_rf_metrics <- fit_rf(data = black_rf_wa, assessment_resamples = black_rf_wa_splits$assessment_resamples)

black_rf_wa_nn_metrics <- fit_nn(data = black_rf_wa, assessment_resamples = black_rf_wa_splits$assessment_resamples)

black_rf_wa_model_comparison_table <- bind_rows(black_rf_wa_null_metrics,
                                              black_rf_wa_lm_metrics,
                                              black_rf_wa_gam_metrics,
                                              black_rf_wa_rf_metrics,
                                              black_rf_wa_nn_metrics)

black_rf_wa_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Black Rockfish (WA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Canary Rockfish (2023 assessment)

```{r canary_rf_ml, cache = TRUE}
canary_rf_splits <- split_training_testing_one_yr_ahead(data = canary_rf)

canary_rf_null_metrics <- fit_null_model(data = canary_rf, testing_resamples_df = canary_rf_splits$testing_resamples_df)

canary_rf_lm_metrics <- fit_lm(data = canary_rf, assessment_resamples = canary_rf_splits$assessment_resamples)

canary_rf_gam_metrics <- fit_gam(data = canary_rf, assessment_resamples = canary_rf_splits$assessment_resamples)

canary_rf_rf_metrics <- fit_rf(data = canary_rf, assessment_resamples = canary_rf_splits$assessment_resamples)

canary_rf_nn_metrics <- fit_nn(data = canary_rf, assessment_resamples = canary_rf_splits$assessment_resamples)

canary_rf_model_comparison_table <- bind_rows(canary_rf_null_metrics,
                                              canary_rf_lm_metrics,
                                              canary_rf_gam_metrics,
                                              canary_rf_rf_metrics,
                                              canary_rf_nn_metrics)

canary_rf_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Canary Rockfish.") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Copper Rockfish - CA, North of Point Conception (2023 assessment)

```{r copper_rf_north_ml, cache = TRUE}
copper_rf_north_splits <- split_training_testing_one_yr_ahead(data = copper_rf_north)

copper_rf_north_null_metrics <- fit_null_model(data = copper_rf_north, testing_resamples_df = copper_rf_north_splits$testing_resamples_df)

copper_rf_north_lm_metrics <- fit_lm(data = copper_rf_north, assessment_resamples = copper_rf_north_splits$assessment_resamples)

copper_rf_north_gam_metrics <- fit_gam(data = copper_rf_north, assessment_resamples = copper_rf_north_splits$assessment_resamples)

copper_rf_north_rf_metrics <- fit_rf(data = copper_rf_north, assessment_resamples = copper_rf_north_splits$assessment_resamples)

copper_rf_north_nn_metrics <- fit_nn(data = copper_rf_north, assessment_resamples = copper_rf_north_splits$assessment_resamples)

copper_rf_north_model_comparison_table <- bind_rows(copper_rf_north_null_metrics,
                                              copper_rf_north_lm_metrics,
                                              copper_rf_north_gam_metrics,
                                              copper_rf_north_rf_metrics,
                                              copper_rf_north_nn_metrics)

copper_rf_north_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Copper Rockfish (Northern CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Copper Rockfish - CA, South of Point Conception (2023 assessment)

```{r copper_rf_south_ml, cache = TRUE}
copper_rf_south_splits <- split_training_testing_one_yr_ahead(data = copper_rf_south)

copper_rf_south_null_metrics <- fit_null_model(data = copper_rf_south, testing_resamples_df = copper_rf_south_splits$testing_resamples_df)

copper_rf_south_lm_metrics <- fit_lm(data = copper_rf_south, assessment_resamples = copper_rf_south_splits$assessment_resamples)

copper_rf_south_gam_metrics <- fit_gam(data = copper_rf_south, assessment_resamples = copper_rf_south_splits$assessment_resamples)

copper_rf_south_rf_metrics <- fit_rf(data = copper_rf_south, assessment_resamples = copper_rf_south_splits$assessment_resamples)

copper_rf_south_nn_metrics <- fit_nn(data = copper_rf_south, assessment_resamples = copper_rf_south_splits$assessment_resamples)

copper_rf_south_model_comparison_table <- bind_rows(copper_rf_south_null_metrics,
                                              copper_rf_south_lm_metrics,
                                              copper_rf_south_gam_metrics,
                                              copper_rf_south_rf_metrics,
                                              copper_rf_south_nn_metrics)

copper_rf_south_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Copper Rockfish (Southern CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Dover Sole (2021 assessment)

```{r dover_sole_ml, cache = TRUE}
dover_sole_splits <- split_training_testing_one_yr_ahead(data = dover_sole)

dover_sole_null_metrics <- fit_null_model(data = dover_sole, testing_resamples_df = dover_sole_splits$testing_resamples_df)

dover_sole_lm_metrics <- fit_lm(data = dover_sole, assessment_resamples = dover_sole_splits$assessment_resamples)

dover_sole_gam_metrics <- fit_gam(data = dover_sole, assessment_resamples = dover_sole_splits$assessment_resamples)

dover_sole_rf_metrics <- fit_rf(data = dover_sole, assessment_resamples = dover_sole_splits$assessment_resamples)

dover_sole_nn_metrics <- fit_nn(data = dover_sole, assessment_resamples = dover_sole_splits$assessment_resamples)

dover_sole_model_comparison_table <- bind_rows(dover_sole_null_metrics,
                                              dover_sole_lm_metrics,
                                              dover_sole_gam_metrics,
                                              dover_sole_rf_metrics,
                                              dover_sole_nn_metrics)

dover_sole_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Dover Sole.") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Lingcod - North of 40°10'N (2021 assessment)

```{r lingcod_north_ml, cache = TRUE}
lingcod_north_splits <- split_training_testing_one_yr_ahead(data = lingcod_north)

lingcod_north_null_metrics <- fit_null_model(data = lingcod_north, testing_resamples_df = lingcod_north_splits$testing_resamples_df)

lingcod_north_lm_metrics <- fit_lm(data = lingcod_north, assessment_resamples = lingcod_north_splits$assessment_resamples)

lingcod_north_gam_metrics <- fit_gam(data = lingcod_north, assessment_resamples = lingcod_north_splits$assessment_resamples)

lingcod_north_rf_metrics <- fit_rf(data = lingcod_north, assessment_resamples = lingcod_north_splits$assessment_resamples)

lingcod_north_nn_metrics <- fit_nn(data = lingcod_north, assessment_resamples = lingcod_north_splits$assessment_resamples)

lingcod_north_model_comparison_table <- bind_rows(lingcod_north_null_metrics,
                                              lingcod_north_lm_metrics,
                                              lingcod_north_gam_metrics,
                                              lingcod_north_rf_metrics,
                                              lingcod_north_nn_metrics)

lingcod_north_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Lingcod (North of 40°10'N).") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Lingcod - South of 40°10'N (2021 assessment)

```{r lingcod_south_ml, cache = TRUE}
lingcod_south_splits <- split_training_testing_one_yr_ahead(data = lingcod_south)

lingcod_south_null_metrics <- fit_null_model(data = lingcod_south, testing_resamples_df = lingcod_south_splits$testing_resamples_df)

lingcod_south_lm_metrics <- fit_lm(data = lingcod_south, assessment_resamples = lingcod_south_splits$assessment_resamples)

lingcod_south_gam_metrics <- fit_gam(data = lingcod_south, assessment_resamples = lingcod_south_splits$assessment_resamples)

lingcod_south_rf_metrics <- fit_rf(data = lingcod_south, assessment_resamples = lingcod_south_splits$assessment_resamples)

lingcod_south_nn_metrics <- fit_nn(data = lingcod_south, assessment_resamples = lingcod_south_splits$assessment_resamples)

lingcod_south_model_comparison_table <- bind_rows(lingcod_south_null_metrics,
                                              lingcod_south_lm_metrics,
                                              lingcod_south_gam_metrics,
                                              lingcod_south_rf_metrics,
                                              lingcod_south_nn_metrics)

lingcod_south_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Lingcod (South of 40°10'N).") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Petrale Sole (2023 assessment)

```{r petrale_sole_ml, cache = TRUE}
petrale_sole_splits <- split_training_testing_one_yr_ahead(data = petrale_sole)

petrale_sole_null_metrics <- fit_null_model(data = petrale_sole, testing_resamples_df = petrale_sole_splits$testing_resamples_df)

petrale_sole_lm_metrics <- fit_lm(data = petrale_sole, assessment_resamples = petrale_sole_splits$assessment_resamples)

petrale_sole_gam_metrics <- fit_gam(data = petrale_sole, assessment_resamples = petrale_sole_splits$assessment_resamples)

petrale_sole_rf_metrics <- fit_rf(data = petrale_sole, assessment_resamples = petrale_sole_splits$assessment_resamples)

petrale_sole_nn_metrics <- fit_nn(data = petrale_sole, assessment_resamples = petrale_sole_splits$assessment_resamples)

petrale_sole_model_comparison_table <- bind_rows(petrale_sole_null_metrics,
                                              petrale_sole_lm_metrics,
                                              petrale_sole_gam_metrics,
                                              petrale_sole_rf_metrics,
                                              petrale_sole_nn_metrics)

petrale_sole_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Petrale Sole.") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Quillback Rockfish - California (2025 assessment)

```{r quillback_rf_ca_ml, cache = TRUE}
quillback_rf_ca_splits <- split_training_testing_one_yr_ahead(data = quillback_rf_ca)

quillback_rf_ca_null_metrics <- fit_null_model(data = quillback_rf_ca, testing_resamples_df = quillback_rf_ca_splits$testing_resamples_df)

quillback_rf_ca_lm_metrics <- fit_lm(data = quillback_rf_ca, assessment_resamples = quillback_rf_ca_splits$assessment_resamples)

quillback_rf_ca_gam_metrics <- fit_gam(data = quillback_rf_ca, assessment_resamples = quillback_rf_ca_splits$assessment_resamples)

quillback_rf_ca_rf_metrics <- fit_rf(data = quillback_rf_ca, assessment_resamples = quillback_rf_ca_splits$assessment_resamples)

quillback_rf_ca_nn_metrics <- fit_nn(data = quillback_rf_ca, assessment_resamples = quillback_rf_ca_splits$assessment_resamples)

quillback_rf_ca_model_comparison_table <- bind_rows(quillback_rf_ca_null_metrics,
                                              quillback_rf_ca_lm_metrics,
                                              quillback_rf_ca_gam_metrics,
                                              quillback_rf_ca_rf_metrics,
                                              quillback_rf_ca_nn_metrics)

quillback_rf_ca_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Quillback Rockfish (CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Rex Sole (2023 assessment)

```{r rex_sole_ml, cache = TRUE}
rex_sole_splits <- split_training_testing_one_yr_ahead(data = rex_sole)

rex_sole_null_metrics <- fit_null_model(data = rex_sole, testing_resamples_df = rex_sole_splits$testing_resamples_df)

rex_sole_lm_metrics <- fit_lm(data = rex_sole, assessment_resamples = rex_sole_splits$assessment_resamples)

rex_sole_gam_metrics <- fit_gam(data = rex_sole, assessment_resamples = rex_sole_splits$assessment_resamples)

rex_sole_rf_metrics <- fit_rf(data = rex_sole, assessment_resamples = rex_sole_splits$assessment_resamples)

rex_sole_nn_metrics <- fit_nn(data = rex_sole, assessment_resamples = rex_sole_splits$assessment_resamples)

rex_sole_model_comparison_table <- bind_rows(rex_sole_null_metrics,
                                              rex_sole_lm_metrics,
                                              rex_sole_gam_metrics,
                                              rex_sole_rf_metrics,
                                              rex_sole_nn_metrics)

rex_sole_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Rex Sole.") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Rougheye/Blackspotted Rockfish (2025 assessment)

```{r rougheye_rf_ml, cache = TRUE}
rougheye_rf_splits <- split_training_testing_one_yr_ahead(data = rougheye_rf)

rougheye_rf_null_metrics <- fit_null_model(data = rougheye_rf, testing_resamples_df = rougheye_rf_splits$testing_resamples_df)

rougheye_rf_lm_metrics <- fit_lm(data = rougheye_rf, assessment_resamples = rougheye_rf_splits$assessment_resamples)

rougheye_rf_gam_metrics <- fit_gam(data = rougheye_rf, assessment_resamples = rougheye_rf_splits$assessment_resamples)

rougheye_rf_rf_metrics <- fit_rf(data = rougheye_rf, assessment_resamples = rougheye_rf_splits$assessment_resamples)

rougheye_rf_nn_metrics <- fit_nn(data = rougheye_rf, assessment_resamples = rougheye_rf_splits$assessment_resamples)

rougheye_rf_model_comparison_table <- bind_rows(rougheye_rf_null_metrics,
                                              rougheye_rf_lm_metrics,
                                              rougheye_rf_gam_metrics,
                                              rougheye_rf_rf_metrics,
                                              rougheye_rf_nn_metrics)

rougheye_rf_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Rougheye/Blackspotted Rockfish") %>% 
  kable_styling(latex_options = "HOLD_position")
```


### Sablefish (2025 assessment)

```{r sablefish_ml, cache = TRUE}
sablefish_splits <- split_training_testing_one_yr_ahead(data = sablefish)

sablefish_null_metrics <- fit_null_model(data = sablefish, testing_resamples_df = sablefish_splits$testing_resamples_df)

sablefish_lm_metrics <- fit_lm(data = sablefish, assessment_resamples = sablefish_splits$assessment_resamples)

sablefish_gam_metrics <- fit_gam(data = sablefish, assessment_resamples = sablefish_splits$assessment_resamples)

sablefish_rf_metrics <- fit_rf(data = sablefish, assessment_resamples = sablefish_splits$assessment_resamples)

sablefish_nn_metrics <- fit_nn(data = sablefish, assessment_resamples = sablefish_splits$assessment_resamples)

sablefish_model_comparison_table <- bind_rows(sablefish_null_metrics,
                                              sablefish_lm_metrics,
                                              sablefish_gam_metrics,
                                              sablefish_rf_metrics,
                                              sablefish_nn_metrics)

sablefish_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Sablefish.") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Vermilion & Sunset Rockfish - Southern CA (2021 assessment)

```{r vermilion_rf_sca_ml, cache = TRUE}
vermilion_rf_sca_splits <- split_training_testing_one_yr_ahead(data = vermilion_rf_sca)

vermilion_rf_sca_null_metrics <- fit_null_model(data = vermilion_rf_sca, testing_resamples_df = vermilion_rf_sca_splits$testing_resamples_df)

vermilion_rf_sca_lm_metrics <- fit_lm(data = vermilion_rf_sca, assessment_resamples = vermilion_rf_sca_splits$assessment_resamples)

vermilion_rf_sca_gam_metrics <- fit_gam(data = vermilion_rf_sca, assessment_resamples = vermilion_rf_sca_splits$assessment_resamples)

vermilion_rf_sca_rf_metrics <- fit_rf(data = vermilion_rf_sca, assessment_resamples = vermilion_rf_sca_splits$assessment_resamples)

vermilion_rf_sca_nn_metrics <- fit_nn(data = vermilion_rf_sca, assessment_resamples = vermilion_rf_sca_splits$assessment_resamples)

vermilion_rf_sca_model_comparison_table <- bind_rows(vermilion_rf_sca_null_metrics,
                                              vermilion_rf_sca_lm_metrics,
                                              vermilion_rf_sca_gam_metrics,
                                              vermilion_rf_sca_rf_metrics,
                                              vermilion_rf_sca_nn_metrics)

vermilion_rf_sca_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Vermilion & Sunset Rockfish (Southern CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Vermilion & Sunset Rockfish - Northern CA (2021 assessment)

```{r vermilion_rf_nca_ml, cache = TRUE}
vermilion_rf_nca_splits <- split_training_testing_one_yr_ahead(data = vermilion_rf_nca)

vermilion_rf_nca_null_metrics <- fit_null_model(data = vermilion_rf_nca, testing_resamples_df = vermilion_rf_nca_splits$testing_resamples_df)

vermilion_rf_nca_lm_metrics <- fit_lm(data = vermilion_rf_nca, assessment_resamples = vermilion_rf_nca_splits$assessment_resamples)

vermilion_rf_nca_gam_metrics <- fit_gam(data = vermilion_rf_nca, assessment_resamples = vermilion_rf_nca_splits$assessment_resamples)

vermilion_rf_nca_rf_metrics <- fit_rf(data = vermilion_rf_nca, assessment_resamples = vermilion_rf_nca_splits$assessment_resamples)

vermilion_rf_nca_nn_metrics <- fit_nn(data = vermilion_rf_nca, assessment_resamples = vermilion_rf_nca_splits$assessment_resamples)

vermilion_rf_nca_model_comparison_table <- bind_rows(vermilion_rf_nca_null_metrics,
                                              vermilion_rf_nca_lm_metrics,
                                              vermilion_rf_nca_gam_metrics,
                                              vermilion_rf_nca_rf_metrics,
                                              vermilion_rf_nca_nn_metrics)

vermilion_rf_nca_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Vermilion & Sunset Rockfish (Northern CA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Vermilion Rockfish - Oregon (2021 assessment)

```{r vermilion_rf_or_ml, cache = TRUE}
vermilion_rf_or_splits <- split_training_testing_one_yr_ahead(data = vermilion_rf_or)

vermilion_rf_or_null_metrics <- fit_null_model(data = vermilion_rf_or, testing_resamples_df = vermilion_rf_or_splits$testing_resamples_df)

vermilion_rf_or_lm_metrics <- fit_lm(data = vermilion_rf_or, assessment_resamples = vermilion_rf_or_splits$assessment_resamples)

vermilion_rf_or_gam_metrics <- fit_gam(data = vermilion_rf_or, assessment_resamples = vermilion_rf_or_splits$assessment_resamples)

vermilion_rf_or_rf_metrics <- fit_rf(data = vermilion_rf_or, assessment_resamples = vermilion_rf_or_splits$assessment_resamples)

vermilion_rf_or_nn_metrics <- fit_nn(data = vermilion_rf_or, assessment_resamples = vermilion_rf_or_splits$assessment_resamples)

vermilion_rf_or_model_comparison_table <- bind_rows(vermilion_rf_or_null_metrics,
                                              vermilion_rf_or_lm_metrics,
                                              vermilion_rf_or_gam_metrics,
                                              vermilion_rf_or_rf_metrics,
                                              vermilion_rf_or_nn_metrics)

vermilion_rf_or_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Vermilion Rockfish (OR).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Vermilion Rockfish - Washington (2021 assessment)

```{r vermilion_rf_wa_ml, cache = TRUE}
vermilion_rf_wa_splits <- split_training_testing_one_yr_ahead(data = vermilion_rf_wa)

vermilion_rf_wa_null_metrics <- fit_null_model(data = vermilion_rf_wa, testing_resamples_df = vermilion_rf_wa_splits$testing_resamples_df)

vermilion_rf_wa_lm_metrics <- fit_lm(data = vermilion_rf_wa, assessment_resamples = vermilion_rf_wa_splits$assessment_resamples)

vermilion_rf_wa_gam_metrics <- fit_gam(data = vermilion_rf_wa, assessment_resamples = vermilion_rf_wa_splits$assessment_resamples)

vermilion_rf_wa_rf_metrics <- fit_rf(data = vermilion_rf_wa, assessment_resamples = vermilion_rf_wa_splits$assessment_resamples)

vermilion_rf_wa_nn_metrics <- fit_nn(data = vermilion_rf_wa, assessment_resamples = vermilion_rf_wa_splits$assessment_resamples)

vermilion_rf_wa_model_comparison_table <- bind_rows(vermilion_rf_wa_null_metrics,
                                              vermilion_rf_wa_lm_metrics,
                                              vermilion_rf_wa_gam_metrics,
                                              vermilion_rf_wa_rf_metrics,
                                              vermilion_rf_wa_nn_metrics)

vermilion_rf_wa_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Vermilion Rockfish (WA).") %>% 
  kable_styling(latex_options = "HOLD_position")
```

### Yellowtail Rockfish (2025 assessment)

```{r yellowtail_rf_ml, cache = TRUE}
yellowtail_rf_splits <- split_training_testing_one_yr_ahead(data = yellowtail_rf)

yellowtail_rf_null_metrics <- fit_null_model(data = yellowtail_rf, testing_resamples_df = yellowtail_rf_splits$testing_resamples_df)

yellowtail_rf_lm_metrics <- fit_lm(data = yellowtail_rf, assessment_resamples = yellowtail_rf_splits$assessment_resamples)

yellowtail_rf_gam_metrics <- fit_gam(data = yellowtail_rf, assessment_resamples = yellowtail_rf_splits$assessment_resamples)

yellowtail_rf_rf_metrics <- fit_rf(data = yellowtail_rf, assessment_resamples = yellowtail_rf_splits$assessment_resamples)

yellowtail_rf_nn_metrics <- fit_nn(data = yellowtail_rf, assessment_resamples = yellowtail_rf_splits$assessment_resamples)

yellowtail_rf_model_comparison_table <- bind_rows(yellowtail_rf_null_metrics,
                                              yellowtail_rf_lm_metrics,
                                              yellowtail_rf_gam_metrics,
                                              yellowtail_rf_rf_metrics,
                                              yellowtail_rf_nn_metrics)

yellowtail_rf_model_comparison_table %>% 
  kbl(caption = "One-year-ahead predictive performance for Yellowtail Rockfish.") %>% 
  kable_styling(latex_options = "HOLD_position")
```


