---
title: "Multivariate analyses"
author: "Markus Min"
date: "`r Sys.Date()`"
output:
  html_document
---

A PCA was run on the tiem series of the 14 predictors (significant PCs of ILD, SSH, SST, and BV; BEUTI north, BEUTI central, CUTI north, CUTI central). None of these predictors had a pairwise Pearson's correlation coefficient of over 0.8 (although many were over 0.7). This PCA is then visualized using the boom/bust/average classification scheme for the recruitment data for each stock.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.height = 12, fig.width = 8)
```


```{r load_data_functions}
library(here)
source(here::here("R", "functions", "load_reformat_data.R"))
```


```{r define_multivariate_analysis_functions}
# correlation structure in our features
feature_cor_mat <- cor(dplyr::select(feature_df, -Yr))

as.data.frame(feature_cor_mat) %>% 
  rownames_to_column("Var1") %>% 
  pivot_longer(cols = -c("Var1"), names_to = "Var2", values_to = "Value") -> feature_cor_values

# feature_cor_values %>%
#   filter(!(Var1 == Var2)) %>% 
#   arrange(desc(abs(Value)))
# corrplot(feature_cor_mat)
# well, some are quite correlated but none are >= 0.8

# Extract only environmental covariates
feature_df %>%
  column_to_rownames("Yr") -> features_only

# run a PCA
features_pca <- prcomp(features_only)
# summary(features_pca)

### function: plot the environmental covariates PCA colored by one stock's recruitment
plot_PCA_recruitment <- function(data, stock_name){
# extra pca scores
as.data.frame(features_pca$x) %>%
  rownames_to_column("Yr") %>%
  mutate(Yr = as.integer(Yr)) %>%
  left_join(data %>% dplyr::select(Yr, one_sd_boom_bust), by = "Yr") %>% 
  filter(!(is.na(one_sd_boom_bust))) -> features_pca_scores_data

# extract loadings
features_pca_loadings <- as.data.frame(features_pca$rotation) %>%
  rownames_to_column("variable") %>%
  dplyr::select(variable, PC1, PC2, PC3)

# Scale loadings for plotting (so arrows fit nicely in the score plot)
loading_scale <- 3
features_pca_loadings <- features_pca_loadings %>%
  mutate(PC1 = PC1 * loading_scale,
         PC2 = PC2 * loading_scale,
         PC3 = PC3 * loading_scale)

# Calculate variance explained
var_explained <- round(100 * features_pca$sdev^2 / sum(features_pca$sdev^2), 1)

# Plot PC1 vs PC2
pc1_pc2_rec_plot <- ggplot() +
  # Year points colored by recruitment category
  geom_point(data = features_pca_scores_data,
             aes(x = PC1, y = PC2, color = one_sd_boom_bust),
             size = 3) +
  # Year labels
  geom_text(data = features_pca_scores_data,
            aes(x = PC1, y = PC2, label = Yr, color = one_sd_boom_bust),
            nudge_y = 0.2, size = 3) +
  # Loading arrows
  geom_segment(data = features_pca_loadings,
               aes(x = 0, y = 0, xend = PC1, yend = PC2),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "gray40") +
  # Loading labels
  geom_text(data = features_pca_loadings,
            aes(x = PC1, y = PC2, label = variable),
            color = "gray40", size = 3, nudge_y = 0.15) +
  # Axis labels with variance explained
  labs(x = paste0("PC1 (", var_explained[1], "%)"),
       y = paste0("PC2 (", var_explained[2], "%)"),
       color = "Recruitment") +
  scale_color_manual(values = c("Average" = "gray60",
                                "Boom" = "steelblue",
                                "Bust" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray80") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray80") +
  theme_minimal() +
  ggtitle(stock_name)

# Plot PC1 vs PC3
pc1_pc3_rec_plot <- ggplot() +
  # Year points colored by recruitment category
  geom_point(data = features_pca_scores_data,
             aes(x = PC1, y = PC3, color = one_sd_boom_bust),
             size = 3) +
  # Year labels
  geom_text(data = features_pca_scores_data,
            aes(x = PC1, y = PC3, label = Yr, color = one_sd_boom_bust),
            nudge_y = 0.2, size = 3) +
  # Loading arrows
  geom_segment(data = features_pca_loadings,
               aes(x = 0, y = 0, xend = PC1, yend = PC3),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "gray40") +
  # Loading labels
  geom_text(data = features_pca_loadings,
            aes(x = PC1, y = PC3, label = variable),
            color = "gray40", size = 3, nudge_y = 0.15) +
  # Axis labels with variance explained
  labs(x = paste0("PC1 (", var_explained[1], "%)"),
       y = paste0("PC3 (", var_explained[3], "%)"),
       color = "Recruitment") +
  scale_color_manual(values = c("Average" = "gray60",
                                "Boom" = "steelblue",
                                "Bust" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray80") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray80") +
  theme_minimal() +
  ggtitle(stock_name)

# Plot PC2 vs PC3
pc2_pc3_rec_plot <- ggplot() +
  # Year points colored by recruitment category
  geom_point(data = features_pca_scores_data,
             aes(x = PC2, y = PC3, color = one_sd_boom_bust),
             size = 3) +
  # Year labels
  geom_text(data = features_pca_scores_data,
            aes(x = PC2, y = PC3, label = Yr, color = one_sd_boom_bust),
            nudge_y = 0.2, size = 3) +
  # Loading arrows
  geom_segment(data = features_pca_loadings,
               aes(x = 0, y = 0, xend = PC2, yend = PC3),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "gray40") +
  # Loading labels
  geom_text(data = features_pca_loadings,
            aes(x = PC2, y = PC3, label = variable),
            color = "gray40", size = 3, nudge_y = 0.15) +
  # Axis labels with variance explained
  labs(x = paste0("PC2 (", var_explained[2], "%)"),
       y = paste0("PC3 (", var_explained[3], "%)"),
       color = "Recruitment") +
  scale_color_manual(values = c("Average" = "gray60",
                                "Boom" = "steelblue",
                                "Bust" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray80") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray80") +
  theme_minimal() +
  ggtitle(stock_name)


pca_rec_plot <- ggarrange(pc1_pc2_rec_plot, pc1_pc3_rec_plot, pc2_pc3_rec_plot,
          nrow = 3, ncol = 1)

return(pca_rec_plot)
}
```


## PCA Visualizations {.tabset .tabset-pills}


### Black Rockfish - Northern CA (2023 assessment)

```{r}
plot_PCA_recruitment(data = black_rf_nca,
             stock_name = "Black Rockfish - Northern CA")
```


### Black Rockfish - Central CA (2023 assessment)

```{r}
plot_PCA_recruitment(data = black_rf_cca,
             stock_name = "Black Rockfish - Central CA")
```


### Black Rockfish - Oregon (2023 assessment)

```{r}
plot_PCA_recruitment(data = black_rf_or,
             stock_name = "Black Rockfish - Oregon")
```


### Black Rockfish - Washington (2023 assessment)

```{r}
plot_PCA_recruitment(data = black_rf_wa,
             stock_name = "Black Rockfish - Washington")
```

### Canary Rockfish (2023 assessment)

```{r}
plot_PCA_recruitment(data = canary_rf,
             stock_name = "Canary Rockfish")
```

### Copper Rockfish - CA, North of Point Conception (2023 assessment)

```{r}
plot_PCA_recruitment(data = copper_rf_north,
             stock_name = "Copper Rockfish - CA, North of Point Conception")
```


### Copper Rockfish - CA, South of Point Conception (2023 assessment)

```{r}
plot_PCA_recruitment(data = copper_rf_south,
             stock_name = "Copper Rockfish - CA, South of Point Conception")
```

### Dover Sole (2021 assessment)

```{r}
plot_PCA_recruitment(data = dover_sole,
             stock_name = "Dover Sole")
```


### Lingcod - North of 40°10'N (2021 assessment)

```{r}
plot_PCA_recruitment(data = lingcod_north,
             stock_name = "Lingcod - North of 40°10'N")
```


### Lingcod - South of 40°10'N (2021 assessment)

```{r}
plot_PCA_recruitment(data = lingcod_south,
             stock_name = "Lingcod - South of 40°10'N")
```


### Petrale Sole (2023 assessment)

```{r}
plot_PCA_recruitment(data = petrale_sole,
             stock_name = "Petrale Sole")
```

### Quillback Rockfish - California (2025 assessment)

```{r}
plot_PCA_recruitment(quillback_rf_ca,
             stock_name = "Quillback Rockfish")
```

### Rex Sole (2023 assessment)

```{r}
plot_PCA_recruitment(data = rex_sole,
             stock_name = "Rex Sole")
```

### Rougheye/Blackspotted Rockfish (2025 assessment)

```{r}
plot_PCA_recruitment(data = rougheye_rf,
             stock_name = "Rougheye/Blackspotted Rockfish")
```


### Sablefish (2025 assessment)

```{r}
plot_PCA_recruitment(data = sablefish,
             stock_name = "Sablefish")
```

### Vermilion & Sunset Rockfish - Southern CA (2021 assessment)

```{r}
plot_PCA_recruitment(data = vermilion_rf_sca,
             stock_name = "Vermilion & Sunset Rockfish - Southern CA")
```

### Vermilion & Sunset Rockfish - Northern CA (2021 assessment)

```{r}
plot_PCA_recruitment(data = vermilion_rf_nca,
             stock_name = "Vermilion & Sunset Rockfish - Northern CA")
```

### Vermilion Rockfish - Oregon (2021 assessment)

```{r}
plot_PCA_recruitment(data = vermilion_rf_or,
             stock_name = "Vermilion Rockfish - Oregon")
```

### Vermilion Rockfish - Washington (2021 assessment)

```{r}
plot_PCA_recruitment(data = vermilion_rf_wa,
             stock_name = "Vermilion Rockfish - Washington")
```

### Yelloweye Rockfish (2025 assessment)

```{r}
plot_PCA_recruitment(data = yelloweye_rf,
             stock_name = "Yelloweye Rockfish")
```


### Yellowtail Rockfish (2025 assessment)

```{r}
plot_PCA_recruitment(data = yellowtail_rf,
             stock_name = "Yellowtail Rockfish")
```
