---
title: "Stock Synthesis Recruitment Estimates"
author: "Markus Min"
date: "`r Sys.Date()`"
output:
  html_document
---
```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(kableExtra)
library(here)
library(mixtools)
library(diptest)
source(here::here("R", "functions", "load_reformat_data.R"))
```

## Background

Recruitment estimates are extracted from [stock assessments conducted within the last five years](https://www.pcouncil.org/stock-assessments-star-reports-stat-reports-rebuilding-analyses-terms-of-reference/groundfish-stock-assessment-documents/). Recruitment estimates were only extracted from assessments where recruitment deviations were estimated in the model. These assessments were all conducted using Stock Synthesis, which estimates annual recruitment in an integrated modeling framework, where recruitment is informed by multiple data sources to the model, but primarily age and length compositions.

The recruitment estimates we are using for this analysis are the log recruitment deviations around a Beverton-Holt stock-recruitment function, with their variability constrained by a parameter called SigmaR, which functions similarly to the standard deviation of a random effect. Recruitment deviations can either be estimated with a constraint where the annual deviations must sum to zero or where this constraint is lifted.

For our stocks, these stocks had a sum to zero constraint:

- Black Rockfish, Central CA (2023)
- Black Rockfish, Northern CA (2023)
- Black Rockfish, OR (2023)
- Black Rockfish, WA (2023)
- Canary Rockfish (2023)
- Dover Sole (2021)
- Lingcod, South of 40°10'N (2021)
- Lingcod, North of 40°10'N (2021)
- Quillback Rockfish, CA (2025)
- Rex Sole (2023)
- Vermilion/Sunset Rockfish, Southern CA (2021)
- Vermilion/Sunset Rockfish, Northern CA (2021)
- Vermilion/Sunset Rockfish, Oregon (2021)
- Vermilion/Sunset Rockfish, Washington (2021)
- Yelloweye Rockfish (2025)
- Yellowtail Rockfish (2025)


These stocks did not have a sum to zero constraint:

- Copper Rockfish, Southern CA (2023)
- Copper Rockfish, Northern CA (2023)
- Petrale Sole (2023)
- Rougheye/Blackspotted Rockfish (2025)
- Sablefish (2025)


#### Boom/bust 

Recruitment is classified into boom, bust, and average categories for the purposes of visualization. These categories were produced by classifying any year with recruitment > 1 SD above the long-term mean a "boom" recruitment event, any year with recruitment < 1 SD below the long-term mean a "bust" recruitment event, and all years within 1 SD of the long-term mean an "average" year. 


```{r define_plot_function}
plot_recr_cat <- function(data, stock_name){
  recr_cat_colors <- c("Bust" = "#762a83",
                       "Average" = "#fee08b",
                       "Boom" = "#006d2c",
                       "Outside bias adjustment" = "gray90")
  
  recr_plot <- ggplot(data, aes(x = Yr, y = Value, color = one_sd_boom_bust)) +
    # geom_line(color = "black", lty = 2) +
    geom_point(size = 3.5) +
    scale_color_manual(values = recr_cat_colors, name = "Boom/Bust Recruitment") +
    scale_x_continuous(breaks = seq(1900, 2020, by = 20)) +
    theme_minimal() +
    ggtitle(stock_name) +
    ylab("Log Recruitment Deviation") +
    xlab("Year") +
    theme(legend.position = c(0.2, 0.8))
  
  return(recr_plot)
}
```


## Categorical recruitment + autocorrelation visualization {.tabset .tabset-pills}


### Black Rockfish - Northern CA (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_nca,
             stock_name = "Black Rockfish - Northern CA")

# plot acf
acf(black_rf_nca$Value)
```


### Black Rockfish - Central CA (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_cca,
             stock_name = "Black Rockfish - Central CA")

# plot acf
acf(black_rf_cca$Value)
```


### Black Rockfish - Oregon (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_or,
             stock_name = "Black Rockfish - Oregon")

# plot acf
acf(black_rf_or$Value)
```


### Black Rockfish - Washington (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_wa,
             stock_name = "Black Rockfish - Washington")

# plot acf
acf(black_rf_wa$Value)
```

### Canary Rockfish (2023 assessment)

```{r}
plot_recr_cat(data = canary_rf,
             stock_name = "Canary Rockfish")

# plot acf
acf(canary_rf$Value)
```

### Copper Rockfish - CA, North of Point Conception (2023 assessment)

```{r}
plot_recr_cat(data = copper_rf_north,
             stock_name = "Copper Rockfish - CA, North of Point Conception")

# plot acf
acf(copper_rf_north$Value)
```


### Copper Rockfish - CA, South of Point Conception (2023 assessment)

```{r}
plot_recr_cat(data = copper_rf_south,
             stock_name = "Copper Rockfish - CA, South of Point Conception")

# plot acf
acf(copper_rf_south$Value)
```

### Dover Sole (2021 assessment)

```{r}
plot_recr_cat(data = dover_sole,
             stock_name = "Dover Sole")

# plot acf
acf(dover_sole$Value)
```


### Lingcod - North of 40°10'N (2021 assessment)

```{r}
plot_recr_cat(data = lingcod_north,
             stock_name = "Lingcod - North of 40°10'N")

# plot acf
acf(lingcod_north$Value)
```


### Lingcod - South of 40°10'N (2021 assessment)

```{r}
plot_recr_cat(data = lingcod_south,
             stock_name = "Lingcod - South of 40°10'N")

# plot acf
acf(lingcod_south$Value)
```


### Petrale Sole (2023 assessment)

```{r}
plot_recr_cat(data = petrale_sole,
             stock_name = "Petrale Sole")

# plot acf
acf(petrale_sole$Value)
```

### Quillback Rockfish - California (2025 assessment)

```{r}
plot_recr_cat(quillback_rf_ca,
             stock_name = "Quillback Rockfish")

# plot acf
acf(quillback_rf_ca$Value)
```

### Rex Sole (2023 assessment)

```{r}
plot_recr_cat(data = rex_sole,
             stock_name = "Rex Sole")

# plot acf
acf(rex_sole$Value)
```

### Rougheye/Blackspotted Rockfish (2025 assessment)

```{r}
plot_recr_cat(data = rougheye_rf,
             stock_name = "Rougheye/Blackspotted Rockfish")

# plot acf
acf(rougheye_rf$Value)
```


### Sablefish (2025 assessment)

```{r}
plot_recr_cat(data = sablefish,
             stock_name = "Sablefish")

# plot acf
acf(sablefish$Value)
```

### Vermilion & Sunset Rockfish - Southern CA (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_sca,
             stock_name = "Vermilion & Sunset Rockfish - Southern CA")

# plot acf
acf(vermilion_rf_sca$Value)
```

### Vermilion & Sunset Rockfish - Northern CA (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_nca,
             stock_name = "Vermilion & Sunset Rockfish - Northern CA")

# plot acf
acf(vermilion_rf_nca$Value)
```

### Vermilion Rockfish - Oregon (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_or,
             stock_name = "Vermilion Rockfish - Oregon")

# plot acf
acf(vermilion_rf_or$Value)
```

### Vermilion Rockfish - Washington (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_wa,
             stock_name = "Vermilion Rockfish - Washington")

# plot acf
acf(vermilion_rf_wa$Value)
```

### Yelloweye Rockfish (2025 assessment)

```{r}
plot_recr_cat(data = yelloweye_rf,
             stock_name = "Yelloweye Rockfish")

# plot acf
acf(yelloweye_rf$Value)
```


### Yellowtail Rockfish (2025 assessment)

```{r}
plot_recr_cat(data = yellowtail_rf,
             stock_name = "Yellowtail Rockfish")

# plot acf
acf(yellowtail_rf$Value)
```



## Recruitment as a mixture

```{r create_table}
# step 1: use dip test to examine when multimodality is supported
black_rf_nca_multimodality_test <- dip.test(black_rf_nca$Value)
black_rf_cca_multimodality_test <- dip.test(black_rf_cca$Value)
black_rf_or_multimodality_test <- dip.test(black_rf_or$Value)
black_rf_wa_multimodality_test <- dip.test(black_rf_wa$Value)
canary_rf_multimodality_test <- dip.test(canary_rf$Value)
copper_rf_north_multimodality_test <- dip.test(copper_rf_north$Value)
copper_rf_south_multimodality_test <- dip.test(copper_rf_south$Value)
dover_sole_multimodality_test <- dip.test(dover_sole$Value)
lingcod_north_multimodality_test <- dip.test(lingcod_north$Value)
lingcod_south_multimodality_test <- dip.test(lingcod_south$Value)
petrale_sole_multimodality_test <- dip.test(petrale_sole$Value)
quillback_rf_ca_multimodality_test <- dip.test(quillback_rf_ca$Value)
rex_sole_multimodality_test <- dip.test(rex_sole$Value)
rougheye_rf_multimodality_test <- dip.test(rougheye_rf$Value)
sablefish_multimodality_test <- dip.test(sablefish$Value)
vermilion_rf_sca_multimodality_test <- dip.test(vermilion_rf_sca$Value)
vermilion_rf_nca_multimodality_test <- dip.test(vermilion_rf_nca$Value)
vermilion_rf_or_multimodality_test <- dip.test(vermilion_rf_or$Value)
vermilion_rf_wa_multimodality_test <- dip.test(vermilion_rf_wa$Value)
yelloweye_rf_multimodality_test <- dip.test(yelloweye_rf$Value)
yellowtail_rf_multimodality_test <- dip.test(yellowtail_rf$Value)

# summarize this in a table
diptest_table <- data.frame(
             stock_name = c("Black Rockfish - Northern CA",
                            "Black Rockfish - Central CA",
                            "Black Rockfish - Oregon",
                            "Black Rockfish - Washington",
                            "Canary Rockfish",
                            "Copper Rockfish - CA, North of Point Conception",
                            "Copper Rockfish - CA, South of Point Conception",
                            "Dover Sole",
                            "Lingcod - North of 40°10'N",
                            "Lingcod - South of 40°10'N",
                            "Petrale Sole",
                            "Quillback Rockfish",
                            "Rex Sole",
                            "Rougheye/Blackspotted Rockfish",
                            "Sablefish",
                            "Vermilion & Sunset Rockfish - Southern CA",
                            "Vermilion & Sunset Rockfish - Northern CA",
                            "Vermilion Rockfish - Oregon",
                            "Vermilion Rockfish - Washington",
                            "Yelloweye Rockfish",
                            "Yellowtail Rockfish"),
             dip.test.p.value = c(black_rf_nca_multimodality_test$p.value,
black_rf_cca_multimodality_test$p.value,
black_rf_or_multimodality_test$p.value,
black_rf_wa_multimodality_test$p.value,
canary_rf_multimodality_test$p.value,
copper_rf_north_multimodality_test$p.value,
copper_rf_south_multimodality_test$p.value,
dover_sole_multimodality_test$p.value,
lingcod_north_multimodality_test$p.value,
lingcod_south_multimodality_test$p.value,
petrale_sole_multimodality_test$p.value,
quillback_rf_ca_multimodality_test$p.value,
rex_sole_multimodality_test$p.value,
rougheye_rf_multimodality_test$p.value,
sablefish_multimodality_test$p.value,
vermilion_rf_sca_multimodality_test$p.value,
vermilion_rf_nca_multimodality_test$p.value,
vermilion_rf_or_multimodality_test$p.value,
vermilion_rf_wa_multimodality_test$p.value,
yelloweye_rf_multimodality_test$p.value,
yellowtail_rf_multimodality_test$p.value))

diptest_table %>% 
  mutate(dip.test.p.value = round(dip.test.p.value, 3)) %>% 
  kbl(caption = "p-values for Hartigan's dip test, where a significant p-value indicates a significantly non-unimodal distribution.") %>% 
  kable_styling(latex_options = "HOLD_position")

```


## Recruitment Histograms + mixtures {.tabset .tabset-pills}


```{r mixture_function}
fit_plot_mixture <- function(data, stock_name){
  mix <- normalmixEM(data$Value, k = 2)
  
  # show the fit
  plot(mix, density=TRUE, cex.axis=1.4, cex.lab=1.4, cex.main=1.8, breaks = 12,
     main2="Recruitment deviations", xlab2="log recDevs", which = 2)
}
```

### Black Rockfish - Northern CA (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_nca,
             stock_name = "Black Rockfish - Northern CA")
```


### Black Rockfish - Central CA (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_cca,
             stock_name = "Black Rockfish - Central CA")
```


### Black Rockfish - Oregon (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_or,
             stock_name = "Black Rockfish - Oregon")
```


### Black Rockfish - Washington (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_wa,
             stock_name = "Black Rockfish - Washington")
```

### Canary Rockfish (2023 assessment)

```{r}
fit_plot_mixture(data = canary_rf,
             stock_name = "Canary Rockfish")
```

### Copper Rockfish - CA, North of Point Conception (2023 assessment)

```{r}
fit_plot_mixture(data = copper_rf_north,
             stock_name = "Copper Rockfish - CA, North of Point Conception")
```


### Copper Rockfish - CA, South of Point Conception (2023 assessment)

```{r}
fit_plot_mixture(data = copper_rf_south,
             stock_name = "Copper Rockfish - CA, South of Point Conception")
```

### Dover Sole (2021 assessment)

```{r}
fit_plot_mixture(data = dover_sole,
             stock_name = "Dover Sole")
```


### Lingcod - North of 40°10'N (2021 assessment)

```{r}
fit_plot_mixture(data = lingcod_north,
             stock_name = "Lingcod - North of 40°10'N")
```


### Lingcod - South of 40°10'N (2021 assessment)

```{r}
fit_plot_mixture(data = lingcod_south,
             stock_name = "Lingcod - South of 40°10'N")
```


### Petrale Sole (2023 assessment)

```{r}
fit_plot_mixture(data = petrale_sole,
             stock_name = "Petrale Sole")
```

### Quillback Rockfish - California (2025 assessment)

```{r}
fit_plot_mixture(quillback_rf_ca,
             stock_name = "Quillback Rockfish")
```

### Rex Sole (2023 assessment)

```{r}
fit_plot_mixture(data = rex_sole,
             stock_name = "Rex Sole")
```

### Rougheye/Blackspotted Rockfish (2025 assessment)

```{r}
fit_plot_mixture(data = rougheye_rf,
             stock_name = "Rougheye/Blackspotted Rockfish")
```


### Sablefish (2025 assessment)

```{r}
fit_plot_mixture(data = sablefish,
             stock_name = "Sablefish")
```

### Vermilion & Sunset Rockfish - Southern CA (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_sca,
             stock_name = "Vermilion & Sunset Rockfish - Southern CA")
```

### Vermilion & Sunset Rockfish - Northern CA (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_nca,
             stock_name = "Vermilion & Sunset Rockfish - Northern CA")
```

### Vermilion Rockfish - Oregon (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_or,
             stock_name = "Vermilion Rockfish - Oregon")
```

### Vermilion Rockfish - Washington (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_wa,
             stock_name = "Vermilion Rockfish - Washington")
```

### Yelloweye Rockfish (2025 assessment)

```{r}
fit_plot_mixture(data = yelloweye_rf,
             stock_name = "Yelloweye Rockfish")
```

### Yellowtail Rockfish (2025 assessment)

```{r}
fit_plot_mixture(data = yellowtail_rf,
             stock_name = "Yellowtail Rockfish")
```