---
title: "Stock Synthesis Recruitment Estimates"
author: "Markus Min"
date: "`r Sys.Date()`"
output:
  html_document
---
```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(kableExtra)
library(here)
library(mixtools)
library(diptest)
source(here::here("R", "functions", "load_reformat_data.R"))
```

## Recruitment Data

Recruitment data will be extracted from the latest stock assessment for a species. This can be an update or a full (benchmark) assessment, but because of the lag for fish actually entering the surveys, no recruitment deviations will be available from the year of the assessment minus the number of years before individuals actually recruit to the stock. For example, for Dover Sole, this is approximately five years. The start of the recruitment time series also coincides with the first years that recruitment is informed by age compositions. For most stocks, this is somewhere around 1970. Stachura et al. 2014 uses 1968 as the first year for most stocks, saying that "we only used stocks and years for which recruitment was estimated (not assumed to perfectly follow a specified stock–recruitment relationship without error) in the analysis." Sablefish first year is 1975.

To determine the years where 



How would we describe recruitment of west coast groundfishes? What would the distribution look like?
- Usually average, 

- episodic recruitment events - where a few year classes dominate the population



Here are the stocks that have been assessed in the last five years. For stocks that have been listed multiple times in the last five years, only the most recent assessment is listed. If we were to go back further in time, we would not have a long period of overlap with the hindcast models.

Given the species listed here, it might be interesting to focus on five or six species that have been recently assessed. Notably, all three species that were the focus of mechanistic investigations of recruitment have all been assessed in the past three years: Pacific Hake (2024), Sablefish (2025), and Petrale Sole (2023). To these three species, we could consider adding some rockfishes.


### Classifying recruitment data

There are many ways to classify estimated recruitment into a categorical response variable. Three potential options are listed below, along with visuals using Petrale sole as an example stock.


#### Stachura et al. 2014

@Stachura2014 examined synchrony in extreme recruitment events among West Coast groundfishes by identifying the years corresponding to the weakest (<25th percentile), average (middle 50th percentile), and strongest (>75th percentile) stock–recruitment residuals for each stock.

#### Boom/bust 

The classification used by @Stachura2014 uses quantiles, which may lead to arbitrary cutoffs between different classifications. For example, as seen in the plot above, this quantile-based approach leads to years with very similar recruitment estimates being assigned to different classifications.

Another way to divide up recruitment into three categories would be to use some sort of cutoff from the distribution of the data to set breakpoints. A simple way to do this would be to call any year with recruitment > 1 SD above the long-term mean a "boom" recruitment event, any year with recruitment < 1 SD below the long-term mean a "bust" recruitment event, and all years within 1 SD of the long-term mean an "average" year. 


#### Episodic recruitment

It has been noted previously that West Coast groundfishes exhibit episodic recruitment, where occasional recruitment events lead to a few year classes dominating the population. To classify recruitment events according to this "episodic recruitment" paradigm, we could use the 1 SD above the long-term mean breakpoint to identify these episodic events, and classify all other years as "baseline" years, where a recruitment event did not occur.

This classification approach shares some similarities with the emerging idea of identifying "bright spots" in conservation and ecology [@Embke2025]. This idea suggests that focusing on these positive outliers can help identify key drivers. This is also, notably, in contrast to the emerging "poor-recruitment paradigm," which asserts that it is easier to identify poor recruitment years than good recruitment years [@Gross2022]. According to the authors, "This approach hypothesizes that it is easier to predict poor recruitment rather than good recruitment because an environmental variable affects recruitment only when its value is extreme (lethal); otherwise, the variable may be benign and not influence recruitment. Thus, good recruitment necessitates all environmental conditions not be harmful and for some to be especially favorable; poor recruitment, however, requires only one environmental variable to be extreme."



##### 2025

- Yellowtail Rockfish
- Sablefish
- Rougheye/Blackspotted Rockfish (cryptic species complex)
- Chilipepper Rockfish
- CA Quillback Rockfish

Note that as of December 10, 2025, the assessment model files for these stocks have not yet been posted on the Council website. However, the assessment model files should be available from the stock assessors if we need them.

##### 2024

- Hake (the assessment files posted on the council website don't have a Report file)

##### 2023

- Yelloweye Rockfish (this is a catch only projection and not a full assessment, and therefore should not be included)
- Widow Rockfish (this is a catch only projection and not a full assessment, and therefore should not be included)
- Shortspine Thornyhead
- Petrale Sole
- CA Copper Rockfish
- Black Rockfish
- Rex Sole
- Canary Rockfish

##### 2021

- Lingcod
- WA Vermilion Rockfish
- OR Vermilion Rockfish
- Northern CA Vermilion and Sunset Rockfish
- Northern CA Vermilion and Sunset Rockfish
- Squarespot Rockfish
- Spiny Dogfish
- Dover Sole
- WA Copper Rockfish
- OR Copper Rockfish


```{r define_plot_function}
plot_recr_cat <- function(data, stock_name){
  recr_cat_colors <- c("Bust" = "#762a83",
                       "Average" = "#fee08b",
                       "Boom" = "#006d2c",
                       "Outside bias adjustment" = "gray90")
  
  recr_plot <- ggplot(data, aes(x = Yr, y = Value, color = one_sd_boom_bust)) +
    # geom_line(color = "black", lty = 2) +
    geom_point(size = 3.5) +
    scale_color_manual(values = recr_cat_colors, name = "Boom/Bust Recruitment") +
    scale_x_continuous(breaks = seq(1900, 2020, by = 20)) +
    theme_minimal() +
    ggtitle(stock_name) +
    ylab("Log Recruitment Deviation") +
    xlab("Year") +
    theme(legend.position = c(0.2, 0.8))
  
  return(recr_plot)
}
```


## Categorical recruitment + autocorrelation visualization {.tabset .tabset-pills}


### Black Rockfish - Northern CA (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_nca,
             stock_name = "Black Rockfish - Northern CA")

# plot acf
acf(black_rf_nca$Value)
```


### Black Rockfish - Central CA (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_cca,
             stock_name = "Black Rockfish - Central CA")

# plot acf
acf(black_rf_cca$Value)
```


### Black Rockfish - Oregon (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_or,
             stock_name = "Black Rockfish - Oregon")

# plot acf
acf(black_rf_or$Value)
```


### Black Rockfish - Washington (2023 assessment)

```{r}
plot_recr_cat(data = black_rf_wa,
             stock_name = "Black Rockfish - Washington")

# plot acf
acf(black_rf_wa$Value)
```

### Canary Rockfish (2023 assessment)

```{r}
plot_recr_cat(data = canary_rf,
             stock_name = "Canary Rockfish")

# plot acf
acf(canary_rf$Value)
```

### Copper Rockfish - CA, North of Point Conception (2023 assessment)

```{r}
plot_recr_cat(data = copper_rf_north,
             stock_name = "Copper Rockfish - CA, North of Point Conception")

# plot acf
acf(copper_rf_north$Value)
```


### Copper Rockfish - CA, South of Point Conception (2023 assessment)

```{r}
plot_recr_cat(data = copper_rf_south,
             stock_name = "Copper Rockfish - CA, South of Point Conception")

# plot acf
acf(copper_rf_south$Value)
```

### Dover Sole (2021 assessment)

```{r}
plot_recr_cat(data = dover_sole,
             stock_name = "Dover Sole")

# plot acf
acf(dover_sole$Value)
```


### Lingcod - North of 40°10'N (2021 assessment)

```{r}
plot_recr_cat(data = lingcod_north,
             stock_name = "Lingcod - North of 40°10'N")

# plot acf
acf(lingcod_north$Value)
```


### Lingcod - South of 40°10'N (2021 assessment)

```{r}
plot_recr_cat(data = lingcod_south,
             stock_name = "Lingcod - South of 40°10'N")

# plot acf
acf(lingcod_south$Value)
```


### Petrale Sole (2023 assessment)

```{r}
plot_recr_cat(data = petrale_sole,
             stock_name = "Petrale Sole")

# plot acf
acf(petrale_sole$Value)
```

### Quillback Rockfish - California (2025 assessment)

```{r}
plot_recr_cat(quillback_rf_ca,
             stock_name = "Quillback Rockfish")

# plot acf
acf(quillback_rf_ca$Value)
```

### Rex Sole (2023 assessment)

```{r}
plot_recr_cat(data = rex_sole,
             stock_name = "Rex Sole")

# plot acf
acf(rex_sole$Value)
```

### Rougheye/Blackspotted Rockfish (2025 assessment)

```{r}
plot_recr_cat(data = rougheye_rf,
             stock_name = "Rougheye/Blackspotted Rockfish")

# plot acf
acf(rougheye_rf$Value)
```


### Sablefish (2025 assessment)

```{r}
plot_recr_cat(data = sablefish,
             stock_name = "Sablefish")

# plot acf
acf(sablefish$Value)
```

### Vermilion & Sunset Rockfish - Southern CA (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_sca,
             stock_name = "Vermilion & Sunset Rockfish - Southern CA")

# plot acf
acf(vermilion_rf_sca$Value)
```

### Vermilion & Sunset Rockfish - Northern CA (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_nca,
             stock_name = "Vermilion & Sunset Rockfish - Northern CA")

# plot acf
acf(vermilion_rf_nca$Value)
```

### Vermilion Rockfish - Oregon (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_or,
             stock_name = "Vermilion Rockfish - Oregon")

# plot acf
acf(vermilion_rf_or$Value)
```

### Vermilion Rockfish - Washington (2021 assessment)

```{r}
plot_recr_cat(data = vermilion_rf_wa,
             stock_name = "Vermilion Rockfish - Washington")

# plot acf
acf(vermilion_rf_wa$Value)
```

### Yellowtail Rockfish (2025 assessment)

```{r}
plot_recr_cat(data = yellowtail_rf,
             stock_name = "Yellowtail Rockfish")

# plot acf
acf(yellowtail_rf$Value)
```



## Recruitment as a mixture

```{r create_table}
# step 1: use dip test to examine when multimodality is supported
black_rf_nca_multimodality_test <- dip.test(black_rf_nca$Value)
black_rf_cca_multimodality_test <- dip.test(black_rf_cca$Value)
black_rf_or_multimodality_test <- dip.test(black_rf_or$Value)
black_rf_wa_multimodality_test <- dip.test(black_rf_wa$Value)
canary_rf_multimodality_test <- dip.test(canary_rf$Value)
copper_rf_north_multimodality_test <- dip.test(copper_rf_north$Value)
copper_rf_south_multimodality_test <- dip.test(copper_rf_south$Value)
dover_sole_multimodality_test <- dip.test(dover_sole$Value)
lingcod_north_multimodality_test <- dip.test(lingcod_north$Value)
lingcod_south_multimodality_test <- dip.test(lingcod_south$Value)
petrale_sole_multimodality_test <- dip.test(petrale_sole$Value)
quillback_rf_ca_multimodality_test <- dip.test(quillback_rf_ca$Value)
rex_sole_multimodality_test <- dip.test(rex_sole$Value)
rougheye_rf_multimodality_test <- dip.test(rougheye_rf$Value)
sablefish_multimodality_test <- dip.test(sablefish$Value)
vermilion_rf_sca_multimodality_test <- dip.test(vermilion_rf_sca$Value)
vermilion_rf_nca_multimodality_test <- dip.test(vermilion_rf_nca$Value)
vermilion_rf_or_multimodality_test <- dip.test(vermilion_rf_or$Value)
vermilion_rf_wa_multimodality_test <- dip.test(vermilion_rf_wa$Value)
yellowtail_rf_multimodality_test <- dip.test(yellowtail_rf$Value)

# summarize this in a table
diptest_table <- data.frame(
             stock_name = c("Black Rockfish - Northern CA",
                            "Black Rockfish - Central CA",
                            "Black Rockfish - Oregon",
                            "Black Rockfish - Washington",
                            "Canary Rockfish",
                            "Copper Rockfish - CA, North of Point Conception",
                            "Copper Rockfish - CA, South of Point Conception",
                            "Dover Sole",
                            "Lingcod - North of 40°10'N",
                            "Lingcod - South of 40°10'N",
                            "Petrale Sole",
                            "Quillback Rockfish",
                            "Rex Sole",
                            "Rougheye/Blackspotted Rockfish",
                            "Sablefish",
                            "Vermilion & Sunset Rockfish - Southern CA",
                            "Vermilion & Sunset Rockfish - Northern CA",
                            "Vermilion Rockfish - Oregon",
                            "Vermilion Rockfish - Washington",
                            "Yellowtail Rockfish"),
             dip.test.p.value = c(black_rf_nca_multimodality_test$p.value,
black_rf_cca_multimodality_test$p.value,
black_rf_or_multimodality_test$p.value,
black_rf_wa_multimodality_test$p.value,
canary_rf_multimodality_test$p.value,
copper_rf_north_multimodality_test$p.value,
copper_rf_south_multimodality_test$p.value,
dover_sole_multimodality_test$p.value,
lingcod_north_multimodality_test$p.value,
lingcod_south_multimodality_test$p.value,
petrale_sole_multimodality_test$p.value,
quillback_rf_ca_multimodality_test$p.value,
rex_sole_multimodality_test$p.value,
rougheye_rf_multimodality_test$p.value,
sablefish_multimodality_test$p.value,
vermilion_rf_sca_multimodality_test$p.value,
vermilion_rf_nca_multimodality_test$p.value,
vermilion_rf_or_multimodality_test$p.value,
vermilion_rf_wa_multimodality_test$p.value,
yellowtail_rf_multimodality_test$p.value))

diptest_table %>% 
  mutate(dip.test.p.value = round(dip.test.p.value, 3)) %>% 
  kbl(caption = "p-values for Hartigan's dip test, where a significant p-value indicates a significantly non-unimodal distribution.") %>% 
  kable_styling(latex_options = "HOLD_position")

```


## Recruitment Histograms + mixtures {.tabset .tabset-pills}


```{r mixture_function}
fit_plot_mixture <- function(data, stock_name){
  mix <- normalmixEM(data$Value, k = 2)
  
  # show the fit
  plot(mix, density=TRUE, cex.axis=1.4, cex.lab=1.4, cex.main=1.8, breaks = 12,
     main2="Recruitment deviations", xlab2="log recDevs", which = 2)
}
```

### Black Rockfish - Northern CA (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_nca,
             stock_name = "Black Rockfish - Northern CA")
```


### Black Rockfish - Central CA (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_cca,
             stock_name = "Black Rockfish - Central CA")
```


### Black Rockfish - Oregon (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_or,
             stock_name = "Black Rockfish - Oregon")
```


### Black Rockfish - Washington (2023 assessment)

```{r}
fit_plot_mixture(data = black_rf_wa,
             stock_name = "Black Rockfish - Washington")
```

### Canary Rockfish (2023 assessment)

```{r}
fit_plot_mixture(data = canary_rf,
             stock_name = "Canary Rockfish")
```

### Copper Rockfish - CA, North of Point Conception (2023 assessment)

```{r}
fit_plot_mixture(data = copper_rf_north,
             stock_name = "Copper Rockfish - CA, North of Point Conception")
```


### Copper Rockfish - CA, South of Point Conception (2023 assessment)

```{r}
fit_plot_mixture(data = copper_rf_south,
             stock_name = "Copper Rockfish - CA, South of Point Conception")
```

### Dover Sole (2021 assessment)

```{r}
fit_plot_mixture(data = dover_sole,
             stock_name = "Dover Sole")
```


### Lingcod - North of 40°10'N (2021 assessment)

```{r}
fit_plot_mixture(data = lingcod_north,
             stock_name = "Lingcod - North of 40°10'N")
```


### Lingcod - South of 40°10'N (2021 assessment)

```{r}
fit_plot_mixture(data = lingcod_south,
             stock_name = "Lingcod - South of 40°10'N")
```


### Petrale Sole (2023 assessment)

```{r}
fit_plot_mixture(data = petrale_sole,
             stock_name = "Petrale Sole")
```

### Quillback Rockfish - California (2025 assessment)

```{r}
fit_plot_mixture(quillback_rf_ca,
             stock_name = "Quillback Rockfish")
```

### Rex Sole (2023 assessment)

```{r}
fit_plot_mixture(data = rex_sole,
             stock_name = "Rex Sole")
```

### Rougheye/Blackspotted Rockfish (2025 assessment)

```{r}
fit_plot_mixture(data = rougheye_rf,
             stock_name = "Rougheye/Blackspotted Rockfish")
```


### Sablefish (2025 assessment)

```{r}
fit_plot_mixture(data = sablefish,
             stock_name = "Sablefish")
```

### Vermilion & Sunset Rockfish - Southern CA (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_sca,
             stock_name = "Vermilion & Sunset Rockfish - Southern CA")
```

### Vermilion & Sunset Rockfish - Northern CA (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_nca,
             stock_name = "Vermilion & Sunset Rockfish - Northern CA")
```

### Vermilion Rockfish - Oregon (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_or,
             stock_name = "Vermilion Rockfish - Oregon")
```

### Vermilion Rockfish - Washington (2021 assessment)

```{r}
fit_plot_mixture(data = vermilion_rf_wa,
             stock_name = "Vermilion Rockfish - Washington")
```

### Yellowtail Rockfish (2025 assessment)

```{r}
fit_plot_mixture(data = yellowtail_rf,
             stock_name = "Yellowtail Rockfish")
```