---
title: "Time series analyses"
author: "Markus Min"
date: "`r Sys.Date()`"
output:
  html_document
---

First, the time series of recruitment for all stocks is shown, using the boom/bust/average classification, to quickly visualize synchrony.

Next, I evaluated synchrony between each pair of stocks using Spearman rank correlation. Significance for these pairwise correlations is evaluated using a t-test, where the sample size used in the calculation is the effective sample size based on the degree of autocorrelation in each time series. An adjusted p-value using the Benjamini-Hochberg False Discovery Rate correction is also presented, given that we are testing 190 different pairwise correlations across our 20 stocks.

Finally, common boom/bust years are identified and visualized on the same PCA of the 14 predictor time series.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.height = 8, fig.width = 8)
```

```{r load_data_functions}
library(here)
library(kableExtra)
library(corrplot)
source(here::here("R", "functions", "load_reformat_data.R"))
```


```{r get_all_data_in_one}
mutate(dplyr::select(black_rf_nca_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Black Rockfish (Northern CA)") %>% 
  bind_rows(mutate(dplyr::select(black_rf_cca_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Black Rockfish (Central CA)")) %>% 
    bind_rows(mutate(dplyr::select(black_rf_or_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Black Rockfish (OR)")) %>% 
    bind_rows(mutate(dplyr::select(black_rf_wa_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Black Rockfish (WA)")) %>% 
    bind_rows(mutate(dplyr::select(copper_rf_north_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Copper Rockfish (North)")) %>% 
    bind_rows(mutate(dplyr::select(copper_rf_south_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Copper Rockfish (South)")) %>% 
    bind_rows(mutate(dplyr::select(canary_rf_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Canary Rockfish")) %>% 
    bind_rows(mutate(dplyr::select(dover_sole_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Dover Sole")) %>% 
    bind_rows(mutate(dplyr::select(lingcod_north_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Lingcod (North)")) %>% 
    bind_rows(mutate(dplyr::select(lingcod_south_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Lingcod (South)")) %>% 
    bind_rows(mutate(dplyr::select(petrale_sole_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Petrale Sole")) %>% 
    bind_rows(mutate(dplyr::select(rex_sole_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Rex Sole")) %>% 
    bind_rows(mutate(dplyr::select(vermilion_rf_sca_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Vermilion Rockfish (Southern CA)")) %>% 
    bind_rows(mutate(dplyr::select(vermilion_rf_nca_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Vermilion Rockfish (Northern CA)")) %>% 
    bind_rows(mutate(dplyr::select(vermilion_rf_or_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Vermilion Rockfish (OR)")) %>% 
    bind_rows(mutate(dplyr::select(vermilion_rf_wa_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Vermilion Rockfish (WA)")) %>% 
    bind_rows(mutate(dplyr::select(quillback_rf_ca_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Quillback Rockfish")) %>% 
    bind_rows(mutate(dplyr::select(sablefish_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Sablefish")) %>% 
    bind_rows(mutate(dplyr::select(rougheye_rf_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Rougheye/Blackspotted Rockfish")) %>% 
    bind_rows(mutate(dplyr::select(yelloweye_rf_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Yelloweye Rockfish")) %>% 
    bind_rows(mutate(dplyr::select(yellowtail_rf_cat_rec, Yr, Value, one_sd_boom_bust), stock = "Yellowtail Rockfish")) -> recdevs_all_long
```

## Synchrony
```{r}
  recr_cat_colors <- c("Bust" = "#762a83",
                       "Average" = "#fee08b",
                       "Boom" = "#006d2c",
                       "Outside bias adjustment" = "gray90")

ggplot(recdevs_all_long, aes(x = Yr, y = stock, fill = one_sd_boom_bust)) +
  geom_tile() +
  scale_fill_manual(values  = recr_cat_colors, name = "Boom/Bust\nRecruitment") +
  scale_y_discrete(limits = rev) +
  theme_minimal()

### Look into Spearman (rank) correlation
# step 1: pivot wider
recdevs_all_long %>% 
  dplyr::select(-one_sd_boom_bust) %>% 
  pivot_wider(names_from = stock, values_from = Value) %>%
  arrange(Yr) %>%
  column_to_rownames("Yr") -> recdevs_wide

# step 2: define ESS helper function
n_eff_pair <- function(x, y) {
  n   <- length(x)
  r1x <- cor(x[-n], x[-1], use = "complete.obs")
  r1y <- cor(y[-n], y[-1], use = "complete.obs")
  n_eff <- n * (1 - r1x * r1y) / (1 + r1x * r1y)
  max(4, floor(n_eff))
}

# step 3: run spearman correlation for each pair of species
sp_pairs <- combn(colnames(recdevs_wide), 2, simplify = FALSE)

results <- map_dfr(sp_pairs, function(pair) {
  x    <- recdevs_wide[[pair[1]]]
  y    <- recdevs_wide[[pair[2]]]
  
  # Use only years where both species have data
  complete <- complete.cases(x, y)
  x <- x[complete]
  y <- y[complete]
  
  rho   <- cor(x, y, method = "spearman")
  neff  <- n_eff_pair(rank(x), rank(y))
  tstat <- rho * sqrt((neff - 2) / (1 - rho^2))
  pval  <- 2 * pt(-abs(tstat), df = neff - 2)
  tibble(sp1 = pair[1], sp2 = pair[2], rho = rho, n_eff = neff, p_raw = pval)
})

# step 4: get adjusted p-values
results <- results %>%
  mutate(p_adj = p.adjust(p_raw, method = "BH"),
         sig   = p_adj < 0.05)

# run it again un-corrected
results <- results %>%
  mutate(sig   = p_raw < 0.05)

# step 5: get symmetric matrices for corrplot
rho_matrix <- matrix(0, ncol(recdevs_wide), ncol(recdevs_wide),
                     dimnames = list(colnames(recdevs_wide), colnames(recdevs_wide)))
diag(rho_matrix) <- 1

sig_matrix <- matrix(TRUE, ncol(recdevs_wide), ncol(recdevs_wide),
                     dimnames = list(colnames(recdevs_wide), colnames(recdevs_wide)))
diag(sig_matrix) <- FALSE

for (i in seq_len(nrow(results))) {
  s1 <- results$sp1[i]; s2 <- results$sp2[i]
  rho_matrix[s1, s2] <- rho_matrix[s2, s1] <- results$rho[i]
  sig_matrix[s1, s2] <- sig_matrix[s2, s1] <- !results$sig[i]
}

# step 6: visualize correlogram
corrplot(rho_matrix,
         method    = "color",
         type      = "upper",
         p.mat     = sig_matrix,
         sig.level = 0.05,
         insig     = "pch",
         pch       = 4,
         pch.cex   = 1.2,
         tl.cex    = 0.6,      # reduced slightly for longer species names
         tl.srt    = 45,       # rotate labels to avoid overlap
         col       = colorRampPalette(c("#2166ac", "white", "#b2182b"))(200),
         # title     = "Pairwise Spearman ρ (X = non-significant after FDR)",
         title     = "Pairwise Spearman ρ (X = non-significant, non-adjusted)",
         mar       = c(0, 0, 2, 0))

# ── 5. Significant pairs summary table ────────────────────────────────────
results %>%
  filter(sig) %>%
  # arrange(desc(abs(rho))) %>%
  arrange(sp1, sp2) %>% 
  dplyr::select(sp1, sp2, rho, n_eff, p_raw, p_adj) %>%
  kbl(caption = "Significant Spearman pairwise correlations for recruitment deviations for pairs of stocks. The raw p-value is the p-value for the t-test using the effective sample size corrected for autocorrelation; the adjusted p-value is the p-value correcting for false positives using the Benjamini-Hochberg FDR correction.") %>% 
  kable_styling(latex_options = "HOLD_position")
```


## Common boom/bust years

```{r}
# which years have the most boom/bust?
as.data.frame(table(recdevs_all_long$Yr,
  recdevs_all_long$one_sd_boom_bust)) %>% 
  pivot_wider(values_from = Freq, names_from = Var2) %>% 
  dplyr::rename(Year = Var1) -> recdevs_allstocks_table

# top five boom years
recdevs_allstocks_table %>% 
  filter(Boom >= 6) %>% 
  arrange(Year) %>% 
  kbl(caption = "Years where 1/3 or more of the stocks had boom recruitment.") %>% 
  kable_styling(latex_options = "HOLD_position")

# top five bust years
recdevs_allstocks_table %>% 
  filter(Bust >= 6) %>% 
  arrange(Year) %>% 
  kbl(caption = "Years where 1/3 or more of the stocks had bust recruitment.") %>% 
  kable_styling(latex_options = "HOLD_position")
```



## PCA showing common boom/bust years

```{r fig.height = 12, fig.width = 8}
# run the same PCA as before
# Extract only environmental covariates
feature_df %>%
  column_to_rownames("Yr") -> features_only

# run a PCA
features_pca <- prcomp(features_only)

# identify top common boom and bust years
bust_years <- as.numeric(as.character(subset(recdevs_allstocks_table, Bust >= 6)$Year))
boom_years <- as.numeric(as.character(subset(recdevs_allstocks_table, Boom >= 6)$Year))


# extra pca scores
as.data.frame(features_pca$x) %>%
  rownames_to_column("Yr") %>%
  mutate(Yr = as.integer(Yr)) %>%
  mutate(common_years = ifelse(Yr %in% bust_years, "Common Bust Year",
                               ifelse(Yr %in% boom_years, "Common Boom Year",
                                      "Normal Year"))) -> features_pca_scores_data

# extract loadings
features_pca_loadings <- as.data.frame(features_pca$rotation) %>%
  rownames_to_column("variable") %>%
  dplyr::select(variable, PC1, PC2, PC3)

# Scale loadings for plotting (so arrows fit nicely in the score plot)
loading_scale <- 3
features_pca_loadings <- features_pca_loadings %>%
  mutate(PC1 = PC1 * loading_scale,
         PC2 = PC2 * loading_scale,
         PC3 = PC3 * loading_scale)

# Calculate variance explained
var_explained <- round(100 * features_pca$sdev^2 / sum(features_pca$sdev^2), 1)

# Plot PC1 vs PC2
pc1_pc2_rec_plot <- ggplot() +
  # Year points colored by recruitment category
  geom_point(data = features_pca_scores_data,
             aes(x = PC1, y = PC2, color = common_years),
             size = 3) +
  # Year labels
  geom_text(data = features_pca_scores_data,
            aes(x = PC1, y = PC2, label = Yr, color = common_years),
            nudge_y = 0.2, size = 3) +
  # Loading arrows
  geom_segment(data = features_pca_loadings,
               aes(x = 0, y = 0, xend = PC1, yend = PC2),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "gray40") +
  # Loading labels
  geom_text(data = features_pca_loadings,
            aes(x = PC1, y = PC2, label = variable),
            color = "gray40", size = 3, nudge_y = 0.15) +
  # Axis labels with variance explained
  labs(x = paste0("PC1 (", var_explained[1], "%)"),
       y = paste0("PC2 (", var_explained[2], "%)"),
       color = "Recruitment") +
  scale_color_manual(values = c("Normal Year" = "gray60",
                                "Common Boom Year" = "steelblue",
                                "Common Bust Year" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray80") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray80") +
  theme_minimal()

# Plot PC1 vs PC3
pc1_pc3_rec_plot <- ggplot() +
  # Year points colored by recruitment category
  geom_point(data = features_pca_scores_data,
             aes(x = PC1, y = PC3, color = common_years),
             size = 3) +
  # Year labels
  geom_text(data = features_pca_scores_data,
            aes(x = PC1, y = PC3, label = Yr, color = common_years),
            nudge_y = 0.2, size = 3) +
  # Loading arrows
  geom_segment(data = features_pca_loadings,
               aes(x = 0, y = 0, xend = PC1, yend = PC3),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "gray40") +
  # Loading labels
  geom_text(data = features_pca_loadings,
            aes(x = PC1, y = PC3, label = variable),
            color = "gray40", size = 3, nudge_y = 0.15) +
  # Axis labels with variance explained
  labs(x = paste0("PC1 (", var_explained[1], "%)"),
       y = paste0("PC3 (", var_explained[3], "%)"),
       color = "Recruitment") +
  scale_color_manual(values = c("Normal Year" = "gray60",
                                "Common Boom Year" = "steelblue",
                                "Common Bust Year" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray80") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray80") +
  theme_minimal()

# Plot PC2 vs PC3
pc2_pc3_rec_plot <- ggplot() +
  # Year points colored by recruitment category
  geom_point(data = features_pca_scores_data,
             aes(x = PC2, y = PC3, color = common_years),
             size = 3) +
  # Year labels
  geom_text(data = features_pca_scores_data,
            aes(x = PC2, y = PC3, label = Yr, color = common_years),
            nudge_y = 0.2, size = 3) +
  # Loading arrows
  geom_segment(data = features_pca_loadings,
               aes(x = 0, y = 0, xend = PC2, yend = PC3),
               arrow = arrow(length = unit(0.2, "cm")),
               color = "gray40") +
  # Loading labels
  geom_text(data = features_pca_loadings,
            aes(x = PC2, y = PC3, label = variable),
            color = "gray40", size = 3, nudge_y = 0.15) +
  # Axis labels with variance explained
  labs(x = paste0("PC2 (", var_explained[2], "%)"),
       y = paste0("PC3 (", var_explained[3], "%)"),
       color = "Recruitment") +
  scale_color_manual(values = c("Normal Year" = "gray60",
                                "Common Boom Year" = "steelblue",
                                "Common Bust Year" = "tomato")) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray80") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray80") +
  theme_minimal()

ggarrange(pc1_pc2_rec_plot, pc1_pc3_rec_plot, pc2_pc3_rec_plot,
          nrow = 3, ncol = 1)

```


